# Explore Data

## Data by Assignment

Data resolved in 2020 by assigment group, measurement is the leadtime, # of day, to resolve the request
Use standard R function: summarise_at
```{r byAssignment, echo=TRUE, message=FALSE, warning=FALSE, comment="", paged.print=TRUE}
# 그룹별 데이터
grp <- "assignment"; col <- "leadtime.day" # leadtime.hour
IT.leadtime <-
  DT %>% filter(resolved >= "2020-01-01" & resolved <= "2020-12-31") %>% 
  group_by(.dots = all_of(grp)) %>% 
  summarise_at(vars(leadtime.day), lst(length,median, mean, sd, max))
IT.leadtime[order(IT.leadtime$length, decreasing = TRUE),] %>% head(20)
```

Use customized function: zdesc.stat2
```{r byAssignment2, echo=TRUE, message=FALSE, warning=FALSE, comment="", paged.print=TRUE}
IT.leadtime2 <-
  DT %>% filter(resolved >= "2020-01-01" & resolved <= "2020-12-31") %>% select(all_of(grp), all_of(col)) %>% 
  group_by(.dots = all_of(grp)) %>% nest() %>% # 동적으로 group by하기 
  mutate(stat = map(data, zdesc.stat2)) %>% 
  unnest(stat) %>% arrange(desc(n))
IT.leadtime2$data <- NULL; IT.leadtime2 <- as_tibble(IT.leadtime2)
IT.leadtime2[order(IT.leadtime2$n, decreasing = TRUE),] %>% head(20)
```

## Data visualization

Leadtime Distribution at glance for all requests in 2020
```{r graph1, echo=FALSE, message=FALSE, warning=FALSE, comment=""}
DT %>% filter(resolved >= "2020-01-01"& resolved <= "2020-12-31") %>% ggplot(aes(x = leadtime.day)) + 
  geom_density(fill = "lightgreen") + scale_x_log10(breaks = c( 1, 5, 10, 20)) +
  labs(title = "Leadtime Distribution", subtitle = "", caption = "", x = "Days", y = "Density") + theme_bw()

```

## Data visualization for top services

Density Plot for Leadtime Distribution 
Most of requests resolved take less than 10 days, and long tail in the graph shows long running tickets to resolve 

```{r graph2, echo=TRUE, message=FALSE, warning=FALSE, comment=""}
i <- 1
assignGrp <- subset(IT.leadtime2,  n > 10000)$assignment
ggplots <- vector('list', length(assignGrp))
for (k in assignGrp) {
  ggplots[[i]] <-
    local({
      data <- DT %>% filter(assignment == k, resolved >= "2020-01-01" & resolved <= "2020-12-31")
      xaxis <- quantile(data$leadtime.day, 0.99,na.rm = T)
      p1 <-  data %>% ggplot(aes(x = leadtime.day)) + 
        geom_density(fill = "lightgreen") + 
        coord_cartesian(xlim = c(0, xaxis)) + labs(subtitle = k, x = "Days", y = "Density") + theme_bw()
      # print(p1)  
    })
  i <- i + 1
}

grid.arrange(ggplots[[1]], ggplots[[8]], nrow = 1)
grid.arrange(ggplots[[3]], ggplots[[12]], nrow = 1)
grid.arrange(ggplots[[10]], ggplots[[11]], nrow = 1)
```

Monthly BoxPlot shows how much lead time varies across months and how many LRT, outlier, each service has
```{r graph3, echo=FALSE, message=FALSE, warning=FALSE, comment=""}
i <- 1
assignGrp <- subset(IT.leadtime2,  n > 10000)$assignment
ggplots <- vector('list', length(assignGrp))
for (k in assignGrp) {
  ggplots[[i]] <-
    local({
      data <- DT %>% filter(assignment == k, resolved >= "2020-01-01" & resolved <= "2020-12-31")
      yaxis <- quantile(data$leadtime.day, 0.99,na.rm = T)
      p1 <-  data %>% ggplot(aes(x = yyyymm, y = leadtime.day, group = yyyymm)) + 
        geom_boxplot() + coord_cartesian(ylim = c(0, yaxis)) + labs(subtitle = k, x = "Month", y = "Day") + theme_bw()
      # print(p1)  
    })
  i <- i + 1
}
grid.arrange(ggplots[[1]], ggplots[[8]], nrow = 1)
grid.arrange(ggplots[[3]], ggplots[[12]], nrow = 1)
grid.arrange(ggplots[[10]], ggplots[[11]], nrow = 1)
```